The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-05-08 paper.Rmd
Make notes of Matt's meeting with TA

# what about therapy?
visits <- read_csv("data/hivvert-data04.csv", progress=FALSE,
                    col_types="iiciiididdiiiiiiiddiiiiiiiiiiiidc") %>%
    # keep MACS only
    filter(COHORT == 1) %>% 
    group_by(STUDYID) %>%
    summarise(drug.use=sum(POTUSE, CRACKUSE, COCUSE, HERUSE, AMPHUSE, 
                           POPUSE, na.rm=TRUE) > 1,
              depression=mean(CESD, na.rm=TRUE) < ifelse(drug.use, 
                                                         16, 23)) %>%
    ungroup() %>%
    # remove the 8 missing depression status
    filter(!is.na(depression))

@@

>>>>

data %>%
    filter(year(death.date) < 2100) %>%
    mutate(time.to.death=difftime(death.date, aids.date, units="weeks") / 4) %>%
    group_by(frst.aids.diag) %>%
    summarise(cases=n(),
              med.to.death=median(time.to.death))

# what about therapy?
visits <- read_csv("data/hivvert-data04.csv", progress=FALSE,
                    col_types="iiciiididdiiiiiiiddiiiiiiiiiiiidc") %>% 
    # keep MACS only
    filter(COHORT == 1) %>% 
    group_by(STUDYID) %>%
    summarise(drug.use=sum(CRACKUSE, COCUSE, HERUSE, AMPHUSE, na.rm=TRUE) > 1,
              depression=mean(CESD, na.rm=TRUE) < 23) %>%
    ungroup() %>%
    # remove the 8 missing depression status
    filter(!is.na(depression))

@@

Keri's recommendations:
    1. Origin being primary diagnosis is fine
    2. person time since prim diag is fine
    3. be careful w/ term time varying exposure
    4. covarites: race is fine, age is fine, remove marijauan and poppers from drug
    5. depression use 23 period.
    6. should depression be mean?
    7. CD4 is great
    8. year of aids diagnosis? restrict to 1996. Censor study at 1996. could
       categorize year (<90, 90-93, 93-Jul 95, >Jul 95)
    9. put people back in that had sec aids at baseline.
    10. timing of secondary aids diagnosis? distribution of prim aids to sec. aids
        infection?
    11. sens. look at dist of survival by type. pick a cutoff that we think is
        meaningful. type of primary. i.e. higher median survival, lower median
        survival.
    12. switch propensity scores to ipw
    13. combinations of prim and sec aids impact. could explore with
        interaction.
    14. Add site
